Icicle: write once, run once

### 2016-06-07 2016fhpc/Main.tex
related
more related work
Wibble to email formatting

\authorinfo{
  Amos Robinson$^{\alpha \beta}$
  \and Ben Lippmeier$^{\beta \gamma}$
}{
  \vspace{5pt}
  \shortstack{
    $^\alpha$Ambiata      \\
    \textsf{amos.robinson@ambiata.com}
  }
  \shortstack{
    $^\beta$UNSW Australia\\
    ~~~~\textsf{amosr,benl@cse.unsw.edu.au}
  }
  \shortstack{
    $^\gamma$Vertigo Technology \\
    ~~\textsf{benl@vergo.co}
  }
}

@@

\input{section/01-Introduction.tex}
\input{section/02-Source.tex}
\input{section/03-Core.tex}
\input{section/04-Benchmarks.tex}
% \input{section/05-Conclusion.tex}
% \input{section/XX-Elimination.tex}
\input{section/XX-Related.tex}

\section*{Acknowledgements}

@@

% \input{section/A1-ExampleDerivation.tex}

>>>>

\authorinfo{
  Amos Robinson$^{\alpha \beta}$
  \and Ben Lippmeier$^{\beta \gamma}$
}{
  \vspace{5pt}
  \shortstack{
    $^\alpha$Ambiata      \\
    \textsf{amos.robinson@ambiata.com}
  }
  \shortstack{
    $^\beta$UNSW Australia\\
    ~~~~\textsf{\{amosr,benl\}@cse.unsw.edu.au}
  }
  \shortstack{
    $^\gamma$Vertigo Technology \\
    ~~\textsf{benl@vergo.co}
  }
}

@@

\input{section/01-Introduction.tex}
\input{section/02-Source.tex}
\input{section/03-Core.tex}
\input{section/04-Benchmarks.tex}
\input{section/XX-Related.tex}

\section*{Acknowledgements}
We are grateful to the entire team at Ambiata; in particular Tran Ma and Jacob Stanley have been indispensable in compiler engineering and performance optimisations.

@@
